Software reliability: Experiences\\ in European scientific research\\ projects and new trends

### 2017-11-07 paper.tex

The software quality procedures \cite{indigo-d31} cover; 1) the identification and description of the \emph{quality requirements} that the software need to comply with, and 2) the \emph{quality metrics}.

>>>>

The software quality procedures \cite{indigo-d31} cover: 1) the identification and description of the \emph{quality requirements} that the software need to comply with, and 2) the \emph{quality metrics}.
